# Data sources

For this analysis, we worked on two major datasets. One is the vegetarian restaurant data and the other is the survey data.

## Vegetarian and vegan restaurants data

We sourced this data from the [data.world](https://data.world/) website. The dataset used for this project is available [here](https://data.world/datafiniti/vegetarian-vegan-restaurants). This dataset contains of around 18000 restaurants that serve vegetarian or vegan food in the US.
Some of the columns used in this project are listed as follows:

- id - id column represents the id of each restaurant.
- address - address of every restaurant
- categories - categories of food items served at each restaurant for example : Seafood, Fish & Seafood Retail
- city - e.g., San Diego - city where the restaurant is located.
- claimed - the websites from which you can order the food.
- country - US for all the restaurants.
- dateAdded - date when the restaurant was opened.
- descriptions - a short description about reviews.
- latitude - latitude of the restaurant.
- longitude - longitude of the restaurant.
- name - name of the restaurant.
- province - abbreviated forms of the states in the United States. For example: California is represented as **CA**.

There are other columns as well but we will be using the columns described above extensively throughout our analysis. The detailed list and description of all the columns in the dataset can be found [here](https://developer.datafiniti.co/docs/business-data-schema).


A sample of the raw data is attached below:
```{r}
library(tidyverse)
library(kableExtra)
df <- read_csv('project_data/vegetarian_restaurants_US_datafiniti.csv')
df <- subset(df, select = -c(menus))
head(df,10) %>% kable(escape = FALSE) %>%
  kable_styling("striped", font_size = 9, full_width = FALSE) %>%
  scroll_box(width = "800px", height ="400px")
```

The number of unique values in each column of the data are listed as follows:
```{r, message=FALSE,warning=FALSE}
library(collapse)
df <- read_csv("project_data/vegetarian_restaurants_US_datafiniti_data.csv")
fNdistinct(df)
```

## Survey Data

This data source was available at the [faunalytics](https://faunalytics.org/) website. A survey was conducted for almost 1500 people who have transitioned or begining to transition into a vegetarian/vegan. The dataset can be found [here](https://faunalytics.org/wp-content/uploads/2017/04/Faunalytics-Current-Former-Veg-Study-Dataset-4-Groups.sav) There a total of 1023 columns in this dataset. The survey was conducted for almost 1387 participants. People from different age groups were invited to take the survey. This survey also contains respondents from different states and cities in the United States. A survey instrument has also been provided to understand the questions in the survey and the respondents answers. The survey instrument can be found [here](https://faunalytics.org/wp-content/uploads/2016/01/Faunalytics-Current-Former-Veg-Study-Survey-Instrument.pdf). The data was made available in the .sav format. We have used the pyreadstat module in python to read the data.
It also contains information about the following: 

- Reasons behind the adoption of vegan/vegetarian diet
- Inconvenience factors that people are facing while transitioning or after the transition
- Age at adoption of vegan/vegetarian diet for every individual in the survey 
- Health and taste concerns .
- Demographic information including race and religion.

The reasons behind the adoption of a vegan/vegetarian diet variables (i.e ANIMALPROTECTION, HEALTH, COST etc.) were designed as 5-point Likert scale response variables through which participants specify their level of agreement to a particular reason. The choices were as follows:

- 1 - Strongly disagree
- 2 - Disagree
- 3 - Neither Agree nor Disagree
- 4 - Agree
- 5 - Strongly Agree

Here is a snapshot of the columns that contain opinion data.

```{r}
df <- read_csv("project_data/Data_sources.csv")
df %>% kable(escape = FALSE) %>%
  kable_styling("striped", font_size = 9, full_width = FALSE) %>%
  scroll_box(width = "800px", height ="400px")
```

The same Likert-scale format was used to capture inconvenience reasons and concerns.
The variable that captures the length that an individual had maintained a vegan/vegetarian diet is recorded as follows:

- 1 - "Up to 3 months"
- 2 - "4–11 months"
- 3 - "1–2 years"
- 4 - "3–5 years" 
- 5 - "6–9 years"
- 6 - "More than 9 years"
- 7 - "Don’t know"

Here is a snapshot of some categorical columns present in the data:

```{r}
df <- read_csv("project_data/Data_source_2.csv")
df %>% kable(escape = FALSE) %>%
  kable_styling("striped", font_size = 9, full_width = FALSE) %>%
  scroll_box(width = "800px", height ="400px")
```

We were also interested in the transition variables that indicates how long an individual take to fully transition into their vegan/vegetarian diet:

- 1 - “1-6 days”
- 2 - “4-11 months”
- 3 - “1-2 years”
- 4 - “3-5 years”
- 5 - “6-10 years”
- 6 - “More than 10 years”
- 7 - “Don’t know


The [SPSS syntax file](https://faunalytics.org/wp-content/uploads/2016/01/Faunalytics-Current-Former-Veg-Study-Syntax-4-Groups.sps) provides a detailed list of all the columns and a short description about each column. This file was used to understand each column in the dataframe.


