# Missing values

```{r}
library(dplyr)
library(naniar)
library(mi)
library(ggplot2)
library(forcats)
library(ggmap)
library(tidyverse)
library(patchwork)
library(janitor)
library(tibble)
```

```{r fig.width=7, fig.height=5}
#df <- read.csv("/Users/saikrupa/Desktop/projects_in_R/data/vegetarian_restaurants_US_datafiniti.csv")
# "/Users/saikrupa/Desktop/projects_in_R/data/Datafiniti_Vegetarian_and_Vegan_Restaurants.csv"
df <- read.csv('project_data/Datafiniti_Vegetarian_and_Vegan_Restaurants.csv')
dat <- df %>% mutate_all(na_if,"")
vis_miss(dat, sort_miss = TRUE, warn_large_data = FALSE) +
  labs(title = "") +
  xlab("")
```
*Observations:*

** 38.3% of all observations in the data are missing while 61.7% of the observations in the data are present.
```{r}
colSums(is.na(dat)) %>% sort(decreasing = TRUE)
```

```{r}
x <- missing_data.frame(dat)
image(x = x)
#summary(x@patterns)
```
*Observations:*

** All of the missing observations observed are from 12 main variables as presented from the map above. 

```{r}
#summary(x@patterns)
```

#### Missing by borough
```{r}
df_b <- dat %>% 
  mutate(Borough = city)
percent_missing <- df_b %>% 
  group_by(Borough) %>% 
  summarize(num_restaurants = n(), num_na_claimed = sum(is.na(`claimed`))) %>% 
  mutate(percent_na = round(num_na_claimed/num_restaurants, 2)) %>% 
  arrange(-percent_na)
```
```{r}
df_b <- dat %>% 
  mutate(Borough = city)
percent_missing <- df_b %>% 
  group_by(Borough) %>% 
  summarize(num_restaurants = n(), num_na_menus_currency = sum(is.na(`menus.currency`))) %>%
  mutate(percent_na = round(num_na_menus_currency/num_restaurants, 2)) %>% arrange(-percent_na)
```

#### Number missing by city

```{r}
missing_counts <- dat %>% group_by(city) %>% summarise_all(~sum(is.na(.))) %>% transmute(city, sumNA = rowSums(.[-1]))
```

```{r fig.width=15, fig.height=20}
ggplot(data=missing_counts, aes(x=fct_reorder(city,-sumNA), y=sumNA)) + 
  geom_bar(stat="identity", color="blue", fill="lightblue") + 
  xlab("City") +
  ylab("Missing count") + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1, size = 25), axis.text.y = element_text(vjust = 0.5, hjust=1, size = 25), axis.title.y =element_text(size = 25), axis.title.x =      element_text(size = 25))
```
*Observations:*

** We examined missing data by city, and interestingly enough, the majority of the missing data counts are those from New York City. 

**Observations from Brooklyn have the second most highest number of missing data. 

#### Function for examining missing data 

```{r fig.size=20}
data.missing <- function(df, percent = 'FALSE'){
  
  missing_patterns <- data.frame(is.na(df)) %>%
  group_by_all() %>%
  count(name = "count", sort = TRUE) %>%
  ungroup()
  if(percent){
  missing_patterns$count = missing_patterns$count*100/nrow(df)
  }
  # Creating New missing patterns dataframe using the old one, this turns the TRUE/FALSE missing data into 1's and 0s. The adorn_totals("col") makes it so that a toal column for the sum of missing patterns in each row is appended to the entire dataframe. 

missing_patterns_new<- missing_patterns %>% mutate_all((as.integer)) %>% adorn_totals("col")

# Creates the pattern identiication. Appends a column called pattern_id that assigns a 0, 0,5, or 1 given the total number missing patterns - the count of missing patterns for each row. This will help in the colors of the overall map
missing_patterns_new <- missing_patterns_new %>%
  mutate(pattern_id=ifelse(missing_patterns_new$Total-missing_patterns_new$count==0,1,0.5))

#Creates a first identification column for each number of rows. there are 9 rows
# This is the final dataframe needed for the entire map
missing_patterns_new <- missing_patterns_new %>% rownames_to_column("id")
missing_patterns_new$id <- as.factor(as.integer(missing_patterns_new$id))

if(percent){
  missing_patterns$count = missing_patterns$count*100/nrow(df)
  p1 <- ggplot(data=missing_patterns_new,aes(x=fct_rev(reorder(id,-count)),y=count)) + 
              geom_bar(aes(alpha=factor(missing_patterns_new$pattern_id)),stat = 'identity',fill = "#03b1fc") + 
              
              xlab("") + ylab("% rows") +
              ylim(0,100) + 
              scale_alpha_manual(values = c("0.5"=0.5,"1.0"=1), guide="none") +
              theme(axis.title.y=element_blank(), legend.position = "none") + 
              coord_flip() +
     theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1, size = 20), axis.text.y = element_text(vjust = 0.5, hjust=1, size = 20), axis.title.y
          =element_text(size = 20), axis.title.x =      element_text(size = 20))
}
else
{
p1 <- ggplot(data=missing_patterns_new,aes(x=fct_rev(reorder(id,-count)),y=count)) + 
              geom_bar(aes(alpha=factor(missing_patterns_new$pattern_id)),stat = 'identity',fill = "#03b1fc") + 
              xlab("") + ylab("row count") +
              scale_alpha_manual(values = c("0.5"=0.5,"1.0"=1), guide="none") +
              theme(axis.title.y=element_blank(), legend.position = "none") + 
              coord_flip() + 
   theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1, size = 20), axis.text.y = element_text(vjust = 0.5, hjust=1, size = 20), axis.title.y
          =element_text(size = 20), axis.title.x =      element_text(size = 20))
}
    

complete_case_id <- missing_patterns_new %>% 
  filter(pattern_id == 1) %>% 
  select(id) %>% 
  as.character()

missing_col <- df %>% select(everything()) %>%
  summarise_all(funs(sum(is.na(.))))


miss_col <- data.frame(col=names(missing_col))

f <- c(missing_col[1,])

miss_col$count <- as.integer(unlist(f))

miss_col <- miss_col[order(-miss_col$count),]

rownames(miss_col) <- 1:nrow(miss_col)

miss_col <- miss_col %>% mutate(col = fct_reorder(col, desc(count)))

if(percent){
  miss_col$count = miss_col$count*100/nrow(df)
  p2 <- ggplot(data= miss_col, aes(x=col,y=count)) + 
  geom_bar(stat = 'identity', fill = "#03b1fc", alpha=0.5) +
  scale_x_discrete(label=function(x) abbreviate(x, minlength = 3)) +
  xlab("") +
  ylim(0,100) + 
  ylab("% rows missing") +
     theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1, size = 20), axis.text.y = element_text(vjust = 0.5, hjust=1, size = 20), axis.title.y
          =element_text(size = 20), axis.title.x =      element_text(size = 20))
}
else{
p2 <- ggplot(data= miss_col, aes(x=col,y=count)) + 
  geom_bar(stat = 'identity', fill = "#03b1fc", alpha=0.5) +
  scale_x_discrete(label=function(x) abbreviate(x, minlength = 3)) +
  xlab("") +
  ylab("num rows missing") + 
   theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1, size = 20), axis.text.y = element_text(vjust = 0.5, hjust=1, size = 20), axis.title.y
          =element_text(size = 20), axis.title.x =      element_text(size = 20))
}

missing_map <- data.frame(is.na(df)) %>% 
  group_by_all() %>%
  count(name = "count", sort = TRUE) %>%
  ungroup()

missing_map <- subset(missing_map, select = -c(count))

tidycars <- missing_map %>% 
  rownames_to_column("id") %>% 
  gather(key, value, -id) %>% #gather key and value except id
  mutate(missing = ifelse(value==1, "yes", "no"))

tidycars <- tidycars %>% mutate(miss2=ifelse(missing=="yes",1,0))

tidycars$miss3 <- as.factor(ifelse(tidycars$id == complete_case_id,0.5,tidycars$miss2))

tidycars$key <- factor(tidycars$key, levels = levels(miss_col$col))
tidycars$id <- factor(tidycars$id, levels = levels(missing_patterns_new$id))

if(complete_case_id == 0) {
g <- ggplot(tidycars, aes(x = key, y = fct_rev(id), fill = miss3)) +
      geom_tile(color = "white") +
      #scale_fill_brewer(palette = "Blues") +
      scale_fill_manual(values=c("#cacaca","#b2a0e1","darkgray")) +
      scale_x_discrete(label=function(x) abbreviate(x, minlength = 3)) +
      xlab("variable") +
      ylab("missing data pattern") +
      #theme(legend.position = "none") + 
  theme(legend.position = "none", axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1, size = 20), axis.text.y = element_text(vjust = 0.5, hjust=1, size = 20), axis.title.y=element_text(size = 20), axis.title.x =      element_text(size = 20)) +
   annotate("text", x=length(unique(tidycars$key))/2, y=complete_case_id, label="complete cases")
}

else{
  g <- ggplot(tidycars, aes(x = key, y = fct_rev(id), fill = miss3)) +
      geom_tile(color = "white") +
      #scale_fill_brewer(palette = "Blues") +
      scale_fill_manual(values=c("#cacaca","#b2a0e1","darkgray")) +
      scale_x_discrete(label=function(x) abbreviate(x, minlength = 3)) +
      xlab("variable") +
      ylab("missing data pattern") +
      #theme(legend.position = "none") + 
  theme(legend.position = "none", axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1, size = 20), axis.text.y = element_text(vjust = 0.5, hjust=1, size = 20), axis.title.y=element_text(size = 20), axis.title.x =      element_text(size = 20))
  
}

p2 + plot_spacer() + g + p1 + plot_layout(widths = c(4,1), heights = c(1,3))

}
```

#### Applying data.missing function to data

```{r fig.width=20, fig.height=15}

data.missing(df, percent = FALSE)

```

```{r fig.width=20, fig.height=15}

data.missing(df, percent = TRUE)

```
*Observations:*

** Based on the resulting maps of missing data, we can note there may be a possibility of there being correlations between the first 9 variables listed on the map, as these variables all seem to have missing data within the same rows. 

** 100% of the data within these rows also appear to be missing.

** The first missing data pattern displayed on the map accounts for just over 60% of the rows in the data

** The second missing data pattern displayed on the map accounts for just over 35% of the rows of the data

** There are no complete cases of no missing data within this dataset.


